Scottish Child Poverty Briefing Plots

### 2024-06-18 minos/outcomes/ChildPovReduction_Combined.Rmd
Small additions to plotting scripts

We use an equation derived from [this paper by Lawrence and Fleishman]() to calculate QALYs from SF-12 MCS and PCS.

>>>>

We use an equation derived from table 4 (below) in [this paper by Lawrence and Fleishman](https://pubmed.ncbi.nlm.nih.gov/15090102/) to calculate QALYs from SF-12 MCS and PCS.

#![L&F Table 4](L&F_table4.png)

```{r}
# formula to find the utility score from mean MCS and PCS scores of a population
utility_score <- function(pcs, mcs) {
  utility_score <- 
    1.6984 + 
    (pcs * 0.07927) +
    (mcs * 0.02859) +
    ((pcs * mcs) * -0.000126) +
    ((pcs * pcs) * -0.00141) +
    ((mcs * mcs) * -0.00014) +
    ((pcs * pcs * pcs) * 0.0000107)
  return(utility_score)
}

# Calculate utility score for hypothetical baseline (MCS & PCS == 45.0)
initial_conditions <- utility_score(pcs = 45.0,
                                    mcs = 45.0)
# Calculate utility score for 0.1 improvement in MCS (MCS now == 45.1)
intervention <- utility_score(pcs = 45.0,
                              mcs = 45.1)

print("Utility score for hypothetical baseline (assuming mean MCS and PCS both equal 45.0):")
print(initial_conditions)
print("Utility score for population given a 0.1 mean improvement in MCS:")
print(intervention)

print("Gain in utility score per person:")
gain <- intervention - initial_conditions
print(gain)

print("Gain in utiliy for the total Scotland population (assuming 5.5m). This is equivalent to QALYs gained:")
print(gain * 5500000)
```
